%% start of file `template.tex'.
%% Copyright 2006-2015 Xavier Danaux (xdanaux@gmail.com), 2020-2026 moderncv maintainers (github.com/moderncv).
%
% This work may be distributed and/or modified under the
% conditions of the LaTeX Project Public License version 1.3c,
% available at http://www.latex-project.org/lppl/.


\documentclass[11pt,a4paper,sans,colorlinks=true]{moderncv}
\moderncvcolor{burgundy}
\moderncvstyle[]{contemporary}
\usepackage[hmargin=0.5in,vmargin=10pt]{geometry}

\ifxetexorluatex
  \usepackage{fontspec}
  \usepackage{unicode-math}
  \defaultfontfeatures{Ligatures=TeX}
  \setmainfont{Latin Modern Roman}
  \setsansfont{Latin Modern Sans}
  \setmonofont{Latin Modern Mono}
  \setmathfont{Latin Modern Math}

\else
  \usepackage[utf8]{inputenc}
  \usepackage[T1]{fontenc}
  \usepackage{lmodern}
\fi

\usepackage[english]{babel}

\name{Szymon}{Zadworny}
\phone[mobile]{+48~721~602~902}
\email{zadworny.code@gmail.com}
\address{}{Gdańsk, Poland}{}

\social[github]{szymon-zadworny}
\social[linkedin]{szymon-zadworny}

\renewcommand*{\bibliographyitemlabel}{[\arabic{enumiv}]}

\begin{document}

\hypersetup{urlcolor=white}

\makecvtitle

\hypersetup{urlcolor=burgundy}

\section{Summary}
Master's student in Informatics specializing in Linux systems programming, distributed systems and computer architecture. Developed communication and leadership skills through long-term research and technical projects. Confident in my abilities, but always eager to learn new skills.


\section{Education}
\cventry{2025--Present}{Master of Engineering in Informatics}{Gdańsk University of Technology}{}{}{Specialization: Machine learning}
\cventry{2021--2025}{Bachelor of Engineering in Informatics}{Gdańsk University of Technology}{}{}{Specialization: Information and communications technology}

\section{Master thesis}
\cvitem{Title}{\emph{Performance analysis of the Finite Element Method implementation in a Web Browser Environment}}
\cvitem{Supervisor}{Marek Moszyński, PhD, DSc Eng.}
\cvitem{Description}{Implementation and performance comparison of FEM algorithms targeting native and WebAssembly environments with WebGPU acceleration.}

\section{Bachelor thesis}
\cvitem{Title}{\emph{Application for anonymous exchange of information using the P2P communication model}}
\cvitem{Supervisor}{Krzysztof Nowicki, PhD Eng.}
\cvitem{Description}{Design and initial Rust-based implementation of a novel anonymizing P2P protocol. I proposed the subject of this thesis and led a team of 4.}

\section{Extracurricular activities}
\cventry{2024--Present}{President}{Vertex Computer Graphics Science Club}{}{}{Created the \link[{\scriptsize \faLink} Rust WebGPU]{https://github.com/szymon-zadworny/vertex-webgpu-course-rs} and \link[{\scriptsize \faLink} C\texttt{++} Dynamic Analysis]{https://github.com/szymon-zadworny/cpp-on-painkillers} courses.}{}
\cventry{2023--2024}{Vice-President}{Vertex Computer Graphics Science Club}{}{}{Assisted a team of 9 people during the \link[{\scriptsize \faLink} Cyberiada 2024-2025]{https://sebhe.itch.io/faster-than-scrap} national game design competition.}{}

\section{Notable Projects}
\cventry{2024--Present}{Main Developer}{\link[{\scriptsize \faLink} Extensible Object Network]{https://github.com/szymon-zadworny/eon} research project}{}{}{A zero-trust distributed database and protocol runtime. A direct continuation of my bachelor thesis.{}
\begin{itemize}
\item Implemented an \link[{\scriptsize \faLink} inversion of control procedural macro layer]{https://github.com/szymon-zadworny/eon/tree/master/libp2p-invert} on top of the Rust libp2p library.
\item Created a custom Kubernetes cluster and a \link[{\scriptsize \faLink} Kustomization-powered testing environment]{https://github.com/szymon-zadworny/eon-k8s}.
\end{itemize}}

\cventry{2025--Present}{Team Lead, Lead Software Architect}{\link[{\scriptsize \faLink} Knot Smart]{https://github.com/Cyberiada2025-2026/Knot-Smart/}}{}{}{A video game for the Cyberiada 2025-2026 national game design competition.{}
\begin{itemize}
\item Effectively managed a team of 10 people using Kanban.
\item Set code review standards and software architecture guidelines.
\item Used profiling and debugging tools to optimize hot code paths.
\end{itemize}}

\section{Languages}
\cvitemwithcomment{Polish}{Native speaker}{}
\cvitemwithcomment{English}{C1 Advanced}{(ACERT, Grade 5.0)}

\section{Programming languages and tools}
\cvitem{Proficient in:}{safe Rust, async Rust, C++17, C, Bash, Python}
\cvitem{Known tools:}{git, binutils, gdb, gprof, lldb, Nix, Kubernetes, CRI-O, Docker, Podman, Shadow}
\end{document}
